Methods and Results

### 2021-03-29 ms.Rmd
Adding loading of metaAidR for I2
Updated bad writing

```{r loadpackages, echo = FALSE, results = "hide"}
  pacman::p_load(tidyverse, metafor, brms)

@@

@@

Overall, we collected effect sizes for a total of `r length(unique(data$species))` species from `r length(unique(data$study))` studies. Unsurprisingly, invertebrates (classes: Insecta, Gastropoda, Malacostraca, Arachnida, Clitellata and Secernentea) made up most of the data (`r (table(inverts$insect)[2] / sum(table(inverts$insect)))*100`%). We obtained `r table(data$Harm_type)[2]` effect sizes where manipulations resulted in changes in direct harm (e.g., XX), whereas `r table(data$Harm_type)[3]` effects came from studies on species that manipulated indirect harm to females. From a total of `r table(data$Harm_type)[1]` effect sizes it was clear that females received both direct and indirect harm from male matings.

Overall, we obtained `r table(data$Gestation)[1]` from `r parity[1,2]` oviparous species, and `r table(data$Gestation)[2]` from `r parity[2,2]`viviparous species. Unfortunately, viviparous species were all fish species with indirect female harm. As such, we analysed only 'harm type' and an index of sexual size dimorphism.

>>>>

```{r loadpackages, echo = FALSE, results = "hide"}
  pacman::p_load(tidyverse, metafor, brms, metaAidR)

@@

  I2(model, v = data$v_SMDH, phylo = FALSE)

@@

Overall, we collected effect sizes for a total of `r length(unique(data$species))` species from `r length(unique(data$study))` studies. Unsurprisingly, invertebrates (classes: Insecta, Gastropoda, Malacostraca, Arachnida, Clitellata and Secernentea) made up most of the data (`r (table(inverts$insect)[2] / sum(table(inverts$insect)))*100`%). We obtained `r table(data$Harm_type)[2]` effect sizes from manipulations on species that resulted in direct harm (e.g., XX), whereas `r table(data$Harm_type)[3]` effects came from studies on species that manipulated indirect harm to females (e.g., mating rate and harassment). A total of `r table(data$Harm_type)[1]` effect sizes were from experiment where females received both direct and indirect harm from male matings.

Across all species, `r table(data$Gestation)[1]` effects were from `r parity[1,2]` oviparous species, and `r table(data$Gestation)[2]` effects were from `r parity[2,2]` viviparous species. Unfortunately, effect sizes from viviparous species were all take from studies on fish species with indirect male harm. As such, we analyzed only 'harm type' and an index of sexual size dimorphism.
